DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/comparison.tex
..

In this section, we compare three computing platforms---the Raspberry
Pi 3, the Intel UP~\footnote{http://www.up-board.org/up/} and NVIDIA
Jetson
TX2~\footnote{http://www.nvidia.com/object/embedded-systems-dev-kits-modules.html}---from
the point of view of supporting vision-based end-to-end deep learning
based autonomous vehicles. 
Table~\ref{tbl:platforms} shows architectural features of the three
platforms~\footnote{Note that the GPUs of the Raspberry Pi 3 and Intel
  Up are not used in evaluation due to lack of software (TensorFlow)
support. Also, the two Denvor cores in Tegra TX2 are not used in
evaluation due to TensorFlow issues.}.

@@

Figure~\ref{fig:sys_core} shows the average control loop completion
timing as a function of the number of CPU cores on each of the four
system configurations.
It was found that the both the Tegra TX2 
and the Intel UP Board performed better than the Raspberry Pi 3 in 
all experiments. On average, the UP was able to perform inferencing 
operations, at least, twice as fast as the Raspberry Pi 3. The 
difference was even greater with the TX2, as control loops, in the 
worst case, were 3x faster using only the CPU and 10x quicker when 
using the GPU. As a result, they were all able to satisfy the 50 ms 
WCET by a very clear margin (in the worst case, the UP Board would 
still meet it by $\sim$20 ms), and, thus, demonstrates that they are 
more capable of autonomous driving than the Raspberry Pi 3.

>>>>

In this section, we compare three computing platforms---the Raspberry
Pi 3, the Intel UP~\footnote{http://www.up-board.org/up/} and NVIDIA
Jetson
TX2~\footnote{http://www.nvidia.com/object/embedded-systems-dev-kits-modules.html}---from
the point of view of supporting vision-based end-to-end deep learning
based autonomous vehicles. 
Table~\ref{tbl:platforms} shows architectural features of the three
platforms~\footnote{Note that the GPUs of the Raspberry Pi 3 and Intel
  Up are not used in evaluation due to the lack of software (TensorFlow)
support. Also, the two Denvor cores in Tegra TX2 are not used in
evaluation due to TensorFlow issues.}.

@@

Figure~\ref{fig:sys_core} shows the average control loop completion
timing as a function of the number of CPU cores on each of the four
system configurations. First, Tegra TX2 and the Intel UP exhibit
superio performance  compared with the Raspberry Pi 3 in 
all experiments. On average, the Intel UP is able to perform
inferencing operations more than twice as fast as the Raspberry Pi
3. The  difference is even greater with the TX2 as the performance is
about 3X faster using only the CPU and 10X faster when using the GPU.
As a result, they were all able to satisfy the 50 ms 
WCET by a very clear margin (in the worst case, the UP Board would 
still meet it by $\sim$20 ms), and, thus, demonstrates that they are 
more capable of autonomous driving than the Raspberry Pi 3.
